Packaging research artefacts with RO-Crate

### 2022-01-01 latex/ro-crate.tex
not directly

In RO-Crate, a referenced contextual entity (e.g. a person identified
by ORCID) should always be described within the RO-Crate Metadata File
with at least a \textit{type} and \textit{name}, even where their PID might resolve
to further Linked Data. This is so that clients are not required to
follow every link for presentation purposes, for instance HTML
rendering. Similarly any imported extension
terms\footnote{\url{https://www.researchobject.org/ro-crate/1.1/appendix/jsonld.html\#extending-ro-crate}}
would themselves also have a human-readable description in the case
where their PID does not resolve to human-readable documentation.

>>>>

In RO-Crate, a referenced contextual entity (e.g. a person identified
by ORCID) should always be described within the RO-Crate Metadata File
with at least a \textit{type} and \textit{name}, even where their PID might resolve
to further Linked Data. This is so that clients are not required to
follow every link for presentation purposes, for instance HTML
rendering. Similarly any imported extension
terms\footnote{\url{https://www.researchobject.org/ro-crate/1.1/appendix/jsonld.html\#extending-ro-crate}}
would themselves also have a human-readable description in the case
where their PID does not directly resolve to human-readable documentation.
